### 2021-04-28 architecture.tex
Make the proof of Lemma 1 typeset well irrespective of font
The typesetting no longer depends on the toggle COMPRESS,
so that restoring the default font will not mess up the formatting.

It is easy to see that all precedences that sort the symbol costs in a non-increasing order
have the same precedence cost.
Since $\argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
each of the precedences in $\argsort^- (c(1), \ldots, c(n))$ has the cost $\min_\rho C(\rho)$.
It follows that $\argsort^- (c(1), \ldots, c(n)) \subseteq \argmin_\rho C(\rho)$.
\qed
\end{proof}

>>>>

To prove the other direction of the equality,
first observe that all precedences $\pi$ that sort the symbol costs in a non-increasing order
necessarily have the same precedence cost $C(\pi)$.
Since
$\emptyset \neq \argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
each of the precedences in $\argsort^- (c(1), \ldots, c(n))$ has the cost $\min_\rho C(\rho)$.
It follows that $\argsort^- (c(1), \ldots, c(n)) \subseteq \argmin_\rho C(\rho)$.
\qed
\end{proof}
